Compositional Equivalences Based on Open pNets

### 2022-09-27 2016-Weak-FH-Bisim/WeakBisim.tex
example

Here is the encoding of a choice operator.\\[1.5ex]
\noindent\begin{tabular}{cp{.45\linewidth}}
 \begin{minipage}{.49\linewidth}
 \includegraphics[width=1.0\linewidth]{XFIG/Choice.pdf}\vspace{-10ex}
\end{minipage} 
&
 It consists of one pNet with two holes and a sub-net. The left hole is
  indexed $L$ the right hole $R$. The sub-net is an labelled transition system (LTS) with three states and emitting actions $l$ and $r$. 
\\
\end{tabular}

@@

\begin{definition}[pNets]\label{def-pnets}
A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes\\
$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
K}\myrangle$
where:
\begin{itemize}
\item[$\bullet$] $I$ is a set of indices and $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$. $vars(P_i)$ and $vars(P_j)$ must be disjoint for $i\neq j$.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

@@

\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
  synchronisation vectors.\\ $\forall k\!\in\! K.\,
  \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ where
  $\alpha'_k\in \AlgAS$, $I_k\subseteq I$, $J_k\subseteq J$,
  $\forall i\!\in\!
  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
$\alpha'_k$. $e_k \in \AlgB$ is a guard associated to the vector such that
$\vars(e_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
\end{itemize}
Synchronisation vectors are identified modulo renaming of variables that appear in their 
action terms.
\end{definition}

>>>>

Here is the encoding of a choice operator.\\[1.5ex]
\noindent\begin{tabular}{cp{.45\linewidth}}
 \begin{minipage}{.49\linewidth}
 \includegraphics[width=1.0\linewidth]{XFIG/Choice.pdf}\vspace{-14ex}
\end{minipage} 
&
 It consists of one pNet (Definition~\ref{def-pnets} below) with two holes and a sub-net. The pNet is represented by the top box with three circles and two synchronisation vectors on the right. The sub-net is a pLTS that is represented by the bottom box. 
\end{tabular}
Each hole is represented by an empty disc, when the hole is filled it becomes a black disc.
The left hole is
  indexed $L$ the right hole $R$. The sub-net is an labelled transition system (LTS) with three states and emitting actions $l$ and $r$.

@@

\begin{definition}[pNets]\label{def-pnets}
A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes \qquad
$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
K}\myrangle$ \qquad
where:
\begin{itemize}
\item[$\bullet$] $I$ is a set of indices and $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$. $vars(P_i)$ and $vars(P_j)$ must be disjoint for $i\neq j$.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

@@

\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
  synchronisation vectors.\\ $\forall k\!\in\! K.\,
  \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ where
  $\alpha'_k\in \AlgAS$, $I_k\subseteq I$, $J_k\subseteq J$,
  $\forall i\!\in\!
  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
$\alpha'_k$. $e_k \in \AlgB$ is a guard associated to the vector such that
$\vars(e_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
\end{itemize}
Synchronisation vectors are identified modulo renaming of variables that appear in their 
action terms, e.g. the vectors $<a(x),b(x)>\to\tau$ and $<a(y),b(y)>\to\tau$ are equivalent.
\end{definition}
